Additional analysis

### 2018-07-19 02_analysis.Rmd
Shrink column titles

```{r tbl-single-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_i,
          diffs_coef_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:amount-single-diffs}") %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-single-diffs.md"))
```

@@

```{r tbl-all-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_ci,
          diffs_coef_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `Crackdown - No crackdown~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between amounts donated in "crackdown" (treatment) and "no crackdown" (control) conditions {#tbl:amount-diffs}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-diffs.md"))
```

@@

```{r tbl-single-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_i,
          diffs_coef_likely_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:likelihood-single-diffs}") %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likelihood-single-diffs.md"))
```

@@

```{r tbl-all-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_ci,
          diffs_coef_likely_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `Crackdown - No crackdown~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between likelihood to donate in "crackdown" (treatment) and "crackdown" (control) conditions {#tbl:likelihood-diffs}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likelihood-diffs.md"))
```

>>>>

```{r tbl-single-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_i,
          diffs_coef_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `%∆~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:amount-single-diffs}") %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-single-diffs.md"))
```

@@

```{r tbl-all-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_ci,
          diffs_coef_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `∆~median~` = median, 
         `%∆~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between amounts donated in "crackdown" (treatment) and "no crackdown" (control) conditions {#tbl:amount-diffs}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-diffs.md"))
```

@@

```{r tbl-single-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_i,
          diffs_coef_likely_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `%∆~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:likelihood-single-diffs}") %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likelihood-single-diffs.md"))
```

@@

```{r tbl-all-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_ci,
          diffs_coef_likely_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `∆~median~` = median, 
         `%∆~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between likelihood to donate in "crackdown" (treatment) and "crackdown" (control) conditions {#tbl:likelihood-diffs}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likelihood-diffs.md"))
```

### 2018-07-19 03_additional-analysis.Rmd
Nicer session info
Shrink column titles

tbl_sample_pop <- calc_sample_pop %>% 
  mutate(in_hpdi = prop_test_bayes %>% map_lgl(~ .$theta_in_hpdi),
         not_hpdi_symbol = ifelse(in_hpdi, "", "^†^"),
         diffs_tidy = prop_test_bayes %>% map(~ .$tidied[2,]),
         diffs_median = diffs_tidy %>% map_dbl(~ .$estimate),
         diffs_hpdi_fancy = diffs_tidy %>%
           map2_chr(.x = diffs_tidy, .y = not_hpdi_symbol, 
                    .f = ~ format_hpdi(.x$conf.low, .x$conf.high, .y))) %>% 
  mutate_at(vars(National, Sample, diffs_median), funs(percent)) %>% 
  select(Variable, Sample, National, 
         `Sample − National~posterior\\ median~` = diffs_median,
         `90% HPDI` = diffs_hpdi_fancy)

@@

# Session info

>>>>

tbl_sample_pop <- calc_sample_pop %>% 
  mutate(in_hpdi = prop_test_bayes %>% map_lgl(~ .$theta_in_hpdi),
         not_hpdi_symbol = ifelse(in_hpdi, "", "^†^"),
         diffs_tidy = prop_test_bayes %>% map(~ .$tidied[2,]),
         diffs_median = diffs_tidy %>% map_dbl(~ .$estimate),
         diffs_hpdi_fancy = diffs_tidy %>%
           map2_chr(.x = diffs_tidy, .y = not_hpdi_symbol, 
                    .f = ~ format_hpdi(.x$conf.low, .x$conf.high, .y))) %>% 
  mutate_at(vars(National, Sample, diffs_median), funs(percent)) %>% 
  select(Variable, Sample, National, 
         `∆~median~` = diffs_median,
         `90% HPDI` = diffs_hpdi_fancy)

@@

# Original computing environment
